---
title: "Cabbages"
author: "Quintin Burnett"
date: "9/3/2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
boxplot(VitC~Cult,data=veggy)
```

Visually yes there is a a difference. I can easily see that the cultivation of "c52" is higher than "c39". The average is a lot higher visually for "c52".

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```

Numerically there is an difference of 7. "c52" has a higher average numerically than "c39". I can deduce with this that "c52" has a higher cultivation than "c32" "c52" 64.4 > "c39" 51.5. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfy the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(VitC~Cult,data=veggy)
```
The percentage value is 0.00000003405 for "c52". I can deduce from this that "c52" has a little chance for having a lower cultivation than "c39". "c52" has a higher cultivation than "c39". 


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Looking at all the information has to offer, I can make the definite decision that "c52" has more cultivation than "c39". Visually the boxplots prove that "c52" has a higher average, Numerically it proves that "c52" has a higher average by 7 while the 1st quartile of "c52" is higher that the 3rd of "c39", and inferentially by its percentage of 0.00000003405.
